---
title: "Assignment week 2"
author: "Bas Kasemir & Rick Venema"
date: "13/5/2018"
output: 
  pdf_document:
    toc: True
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


# Introduction
Corticosteroids are adrenal cortex hormones. There are two groups where the corticoteroids can be divided in: Glucocorticoids and Mineralocorticoids. The 
corticosteroids are used in the treatments against several diseases related to skin and  allergies because they act on for example the nasel passage epithelial cells and on the T Lymfocytes.
The cell membrame of these cells is composed of glucocorticoid dissolving lipids. The glucocorticoid crosses the cell membrame and is roaming in the cytoplasm. It will bind eventually to a GR (glucocorticoid receptor). When these two complexes are binded together by a ligand binding, the GR complex gets activated by binding to AP-1. This inhibits the response to chemical messengers like inflammatory cytokines. The complex could also moves towards the nucleus. There the complex will bind to glucocorticoid response elements on the DNA and thereby control protein production. It deregulates pro-inflammatory cytokine productions and up-regulates anti inflammatory protein production.

# Materials and Methods

## The Model
The model gives the expression of glucocorticoid receptors, where down-regulation occurs due to the presence of corticosterone. 

## FLOW DIAGRAM

## Functions

$$ \frac {dmRNA_{R}}{dt} = k_{s\_Rm}\ \biggl(1-\frac {DR(N)}{IC_{50\_Rm} +DR(N)}\biggr) - k_{d\_Rm} * mRNA_{R} $$

$$\frac {dR}{dt} = k_{s\_R} * mRNA_{R} + R_{f} * k_{re} * DR(N) - k_{on} * D *R - k_{d\_R} * R   $$

$$\ \frac {dDR}{dt} = k_{on} * D * R - k_{\tau} * DR $$

$$\ \frac {dDRN(N)}{dt} = k_{\tau} *DR - k_{re} *DR(N)  $$


## Table of parameters and startingvalues

## Wat er gedaan is



# Results
```{r model, echo= F}

# Rick Venema
# 368044
# k.f.venema@st.hanze.nl

########
# Libs #
########
library(deSolve)

#############
# functions #
#############

# Define the parameters
parameters <- c(kd_Rm = 0.612, ks_Rm = 2.90, ks_r = 3.22, kd_R = 0.0572, D=53.409, k_on= 0.00329, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57, Rf = 0.49) 


# Define the model function
volume <- function(t, y, parms){
  with(as.list(c(y, parms)), {
    dmRNA.R_dt <- ks_Rm * (1- (DR_N/ (IC50_Rm + DR_N)))- kd_Rm * mRNA.R 
    dR_dt <- ks_r *  mRNA.R + Rf * k_re * DR_N - k_on * D * R - kd_R * R
    dDR_dt <- k_on * D * R -k_t * DR
    dDR_N_dt <- k_t * DR - k_re* DR_N
    return(list(c(dmRNA.R_dt, dR_dt, dDR_N_dt, dDR_dt)))
  }
  )
}

# Define the state
state <- c(mRNA.R = 4.74, R = 267, DR_N = 0, DR = 0)

# Define time sequence you want to run the model
times <- seq(0, 48,  by = 1)

# Run simulation using continuous approach
out  <- ode(times = times, y = state,   parms = parameters, func = volume, method = "euler")



```



```{r plotR (a), echo=FALSE, fig.cap="Graph showing the concentration of receptors in the cell during a 48 hour time period"}
plot(out[,'R'], type="l", xlab="timeunits (hours)", ylab="[R]", main="Concentration of receptors in the cell")
```
In this graph the concentration of receptors in the cell are shown. This graph is a declining graph meaning that the concentration of the receptors decreases. This is caused by 
\newpage

```{r plot MPL (b), echo=FALSE, fig.cap="Graph showing the concentration of the MPL-receptor complex in the cell duringa 48 hour time period"}
plot(out[, 'DR'], type="l", xlab="timeunits (hours)", ylab="[DR]")
title(main="Concentration of MPL-receptor complex in the cell")
```

\newpage

```{r plot activated MPL (c), echo=FALSE, fig.cap = "Graph showing the concentration of the activated MPL-receptor complex in the nucleus during a 48 hour time period"}
plot(out[, 'DR_N'], type="l", xlab="timeunits (hours)", ylab="[DR(N)]")
title(main="Concentration of activated MPL-receptor complex \n in the nucleus ")
```

\newpage

```{r plot mRNA (d), echo=FALSE, fig.cap= "Graph showing the concentration of the free receptor mRNA in the cell during a 48 hour time period"}
plot(out[,'mRNA.R'], type="l", xlab="timeunits (hours)", ylab="[mRNA]")
title(main="Concentration of the free receptor mRNA in the cell")
```

\newpage

# Disussion


# Attachements
HIER MOET DE CODE KOMEN TE STAAN

