---
title: "Assignment week 3"
author: "Bas Kasemir & Rick Venema"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: yes
    fig_caption: yes
header-includes:
- \usepackage{float}
- \usepackage{graphicx}
- \usepackage{caption}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.pos='H')
```

\newpage
# Introduction
Corticosteroids are adrenal cortex hormones. There are two groups where the corticoteroids can be divided in: Glucocorticoids and Mineralocorticoids. The
corticosteroids are used in the treatments against several diseases related to skin and  allergies because they act on for example the nasel passage epithelial cells and on the T Lymfocytes.
The cell membrame of these cells is composed of glucocorticoid dissolving lipids. The glucocorticoid crosses the cell membrame and is roaming in the cytoplasm. It will bind eventually to a GR (glucocorticoid receptor). When these two complexes are binded together by a ligand binding, the GR complex gets activated by binding to AP-1. This inhibits the response to chemical messengers like inflammatory cytokines. The complex could also moves towards the nucleus. There the complex will bind to glucocorticoid response elements on the DNA and thereby control protein production. It deregulates pro-inflammatory cytokine productions and up-regulates anti inflammatory protein production.


# The Model

## About the model
The model gives the expression of glucocorticoid receptors, where down-regulation occurs due to the presence of corticosterone. The drug contains the hormone corticosterone. These hormones are presented to the cell, go inside the cell and eventually bind to the glucocorticoid receptor in the cells DNA and reduce the chance of an inflammatory reaction.
MDL is the drug. mRNAR is the receptor.
The greater the D concentration, the more DR(N) there wil be. This will lower ks_RM because less will be transcribed, because the complex has bonded to the glucocorticoid in the DNA. However, kd_Rm will get greater because the concentration of GR mRNA will get bigger and these two will stay in balance.

## Functions

$$ \frac {dmRNA_{R}}{dt} = k_{s\_Rm}\ \biggl(1-\frac {DR(N)}{IC_{50\_Rm} +DR(N)}\biggr) - k_{d\_Rm} * mRNA_{R} $$

$$\frac {dR}{dt} = k_{s\_R} * mRNA_{R} + R_{f} * k_{re} * DR(N) - k_{on} * D * R - k_{d\_R} * R   $$

$$\ \frac {dDR}{dt} = k_{on} * D * R - k_{\tau} * DR $$

$$\ \frac {dDRN(N)}{dt} = k_{\tau} * DR - k_{re} * DR(N)  $$


## Validation of the model
To validate the model data from experiments is used to assess the model. If the experiment data is added, the model can
show graphs having the same course, meaning that the model is acurate. If the model shows the same course, but is slightly 
higher or lower than the experiment data, we can conclude that the model is not refined yet, and needs tweaking of the 
parameters to give a better representation of the reality.

\newpage
# Results

## Model results


```{r model, echo= F}

# Rick Venema
# 368044
# k.f.venema@st.hanze.nl

########
# Libs #
########
library(deSolve)

#############
# functions #
#############

# Define the parameters
parameters <- c(kd_Rm = 0.612, ks_Rm = 2.90, ks_r = 3.22,
                kd_R = 0.0572, D=53.409, k_on= 0.00329, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57, Rf = 0.49)


# Define the model function
volume <- function(t, y, parms){
  with(as.list(c(y, parms)), {
    dmRNA.R_dt <- ks_Rm * (1- (DR_N/ (IC50_Rm + DR_N)))- kd_Rm * mRNA.R
    dR_dt <- ks_r *  mRNA.R + Rf * k_re * DR_N - k_on * D * R - kd_R * R
    dDR_dt <- k_on * D * R -k_t * DR
    dDR_N_dt <- k_t * DR - k_re* DR_N
    return(list(c(dmRNA.R_dt, dR_dt, dDR_N_dt, dDR_dt)))
  }
  )
}

# Define the state
state <- c(mRNA.R = 4.74, R = 267, DR_N = 0, DR = 0)

# Define time sequence you want to run the model
times <- seq(0, 48,  by = 1)

# Run simulation using continuous approach
out <- ode(times = times, y = state,   parms = parameters, func = volume, method = "euler")
out <- as.data.frame(out)
```

In figure 1a, the concentration of receptor mRNA in the cell is shown. This graph is a declining graph meaning that the concentration of the receptors decreases. This is caused by the activation of these receptors.
And after a while the concentration increases, meaning that the concentration of receptor mRNA increases until it reaches an equilibrium. This increase is due to the loss of activated receptor in the nucleus.

As shown in figure 1b, the concentration of free receptors decreases in the cell, this is because almost all the glucocorticoid receptor binds with glucocorticoid that enters the cell. Eventually this graph reaches it
equilibrium nearing zero. This is because of the down-regulation of their own receptors.

Figure 1c, and figure 1d have the same course, this is because they have a correlation. Figure 1c shows the drug-receptor complex in the cell itself and figure 1d shows the activated receptor complex. This last complex
moves to the nucleus of the cell, meaning that the graph in figure 1d has a slight move to the right. This is because it takes some time for an activated receptor complex to move to the nucleus of the cell.
  
```{r plots, echo=F, fig.cap="Graphs showing the concentration of receptors in the cell during a 48 hour time period", fig.pos="!hb"}
par(mfrow = c(2, 2))

plot(out$time,out$mRNA.R,ylim = c(0,5), xlab="Time",
     ylab="receptor mRNA",type="l",lwd=2,
     sub="(a)",
     main = "Concentration of the receptor mRNA in the cell",
     cex.main=0.7)

plot(out$time,out$R, ylim = c(0,500), xlab="Time",
     ylab="free receptor density",type="l",lwd=2,
     sub="(b)",
     main = "Concentration of free receptors in the cell",
     cex.main = 0.7)

plot(out$time,out$DR, ylim = c(0,75), xlab="Time",ylab="drug-receptor complex",type="l",lwd=2,
     sub="(c)",
     main="Concentration of MPL-receptor complex in the cell",
     cex.main=0.7)

plot(out$time,out$DR_N, ylim = c(0,75), xlab="Time",ylab="activated receptor complex",type="l",lwd=2,
     sub="(d)",
     main = "Concentration of activated MPL-receptor complex \n in the nucleus",
     cex.main=0.7)



```


\newpage
## Model validation

```{r model validation, echo = F}
# Rick Venema
# 368044
# k.f.venema@st.hanze.nl

############
# The Data #
############
# Read data from CSV file
data <- read.csv("MPL.csv", na.strings = "NA")

# Store trimmed data for dose 0.1 and dose 0.3
data_0.1 <- data[data$dose == 0.1,]
data_0.3 <- data[data$dose == 0.3,]

# Calculate the median of the cocentration MPL for dose 0.1 and dose 0.3
median_MPL_0.3 <- median(data$MPL_conc[data$dose==0.3], na.rm = T)
median_MPL_0.1 <- median(data$MPL_conc[data$dose==0.1], na.rm = T)

# Store trimmed data for dose 0.1 and dose 0.3
D_0.3 <- median_MPL_0.3*1000/374.471
D_0.1 <- median_MPL_0.1*1000/374.471

####
# Model with parameters responding with experiment
#
parameters0.3 <- c(kd_Rm = 0.612, ks_Rm = 2.90, ks_r = 3.22,
                kd_R = 0.0572, D= D_0.3, k_on= 0.00329, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57, Rf = 0.49)

parameters0.1 <- c(kd_Rm = 0.612, ks_Rm = 2.90, ks_r = 3.22,
                kd_R = 0.0572, D= D_0.1, k_on= 0.00329, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57, Rf = 0.49)

state0.3 <- c(mRNA.R = 4.74, R = 267, DR_N = 0, DR = 0)
state0.1 <- c(mRNA.R = 4.74, R = 267, DR_N = 0, DR = 0)

times <- seq(0, 175,  by = 1)


# Run simulation using continuous approach
out0.3  <- ode(times = times, y = state0.3,   parms = parameters0.3, func = volume, method = "euler")
out0.3 <- as.data.frame(out0.3)

out0.1  <- ode(times = times, y = state0.1,   parms = parameters0.1, func = volume, method = "euler")
out0.1 <- as.data.frame(out0.1)

medians <- aggregate(data[,c("MPL_conc","mRNA","Free_receptor")],list(data$dose,data$time), median, na.rm=T)
names(medians)[1:2] <- c("dose","time")

dose_0.3 <- medians[medians$dose==0.3,]
dose_0.1 <- medians[medians$dose==0.1,]
```
  

In figure 2a and 2b the model is shown with the experimental data. By adding this data, the model can be
validated. In these graphs, the model is represented as the black line, the medians are represented by the red
line, and the black dots are representing the raw experimental data. As shown in the graph, the median line follows the 
model line, exept for around 50 hours. On timepoint 50, there is a little bump in the line, this means that the
average on that timepoint is a bit higher than expected from the model. Furthermore there is a clear difference
in figure 2a the line gets a lower steady point than the model in figure 2b, this is due to the lowering of the dose. A higher dose results in a lower concentration of free receptor in the cell.
  

  
```{r plots validation, echo=F, fig.cap="Graphs showing the experiment data in combination with the model", fig.height=3.5, fig.pos='!H'}
# parameters to define the layout of the figure
par(mfrow=c(1,2))

# Plots of Free receptor
plot(dose_0.3$time, dose_0.3$Free_receptor, ylim=c(0,500), col="red", type="l", xlim=c(-1, 175),
     main="Concentration of Free receptor \n with dose 0.3",
     sub = "(a)", xlab = "Timeunits", ylab = "Free receptor",
     cex.main = 1)
points(data_0.3$time,data_0.3$Free_receptor)
points(out0.3$time,out0.3$R, type="l")

plot(dose_0.1$time, dose_0.1$Free_receptor, ylim=c(0,500), col="red", type="l", xlim=c(-1, 175),
     main="Concentration of Free receptor \n with dose 0.1", 
     sub = "(b)", xlab = "Timeunits", ylab="Free receptor",
     cex.main = 1)
points(data_0.1$time,data_0.1$Free_receptor)
points(out0.1$time,out0.1$R, type="l")
```
  
Figure 3 shows the difference in concentration of mRNA with dose 0.3 and dose 0.1, This difference is visable in the height of the steady state of the model. With a dose 0.3 the steady state is lower than the steady state of dose 0.1. This can be seen in figure 3a and figure 3b. After the model has entered the steady state, the 
experimental data is not a straight steady state. The experimental data has a big fluctuation. 

```{r plots validation mRNA, echo=F, fig.cap="The difference in concentration of mRNA by dose 0.1 and dose 0.3", fig.height=3.5, fig.pos='!Ht'}
par(mfrow=c(1,2))
# Plots of concentration mRNA
plot(dose_0.3$time, dose_0.3$mRNA, col="red", type="l", xlim=c(-1, 175),
     main = "Concentration of mRNA \n with dose 0.3",
     sub = "(a)", xlab = "Timeunits", ylab = "mRNA",
     cex.main = 1 )
points(data_0.3$time,data_0.3$mRNA)
points(out0.3$time,out0.3$mRNA.R, type="l")

plot(dose_0.1$time, dose_0.1$mRNA, col="red", type="l", xlim=c(-1, 175),
     main="Concentration of mRNA with \n dose 0.1",
     sub = "(b)", xlab = "Timeunits", ylab="mRNA",
     cex.main = 1)
points(data_0.1$time,data_0.1$mRNA)
points(out0.1$time,out0.1$mRNA.R, type="l")
```
  
Figure 4 shows the difference of concentration of MPL with dose 0.3 and dose 0.1. In figure 4a the model shows a completely different path than the experiment data. 
This means that the model is not representative of the reality and thus can be further improved to match the experiment data. Figure 4b model line shows the same course as the experiment data, meaning that the model is acurate and is in line
with the experiment data.


```{r plots validation MPL, echo=F, fig.cap="Figure showing the difference in concentration of MPL with dose 0.3 and dose 0.1", fig.height=3.5, fig.pos='!Ht'}
par(mfrow=c(1,2))
# Plots of concentration MPL
plot(dose_0.3$time, dose_0.3$MPL_conc, col="red", type="l", ylim=c(0,150), xlim=c(-1, 175),
     main = "Concentration of MPL \n with dose 0.3",
     sub = "(a)", xlab = "Timeunits", ylab = "MPL",
     cex.main = 1)
points(data_0.3$time, data_0.3$MPL_conc)
points(out0.3$time, out0.3$DR, type="l")

plot(dose_0.1$time, dose_0.1$MPL_conc, col="red", type="l", ylim=c(0,150), xlim=c(-1, 175),
     main = "Concentration of MPL \n with dose 0.1",
     sub = "(b)", xlab = "Timeunits", ylab = "MPL",
     cex.main = 1)
points(data_0.1$time, data_0.1$MPL_conc)
points(out0.1$time, out0.1$DR, type="l")
```


\newpage
# Bibliografie
1. Meijsing, Sebastiaan H. et al. The Ligand Binding Domain Controls Glucocorticoid Receptor Dynamics Independent of Ligand Release Molecular and Cellular Biology 27.7 (2007): 2442 2451. PMC. Web. 18 May 2018.
2. Writing Your Thesis with R Markdown (5) - The Thesis Layout https://rosannavanhespenresearch.wordpress.com/2016/03/30/writing-your-thesis-with-r-markdown-5-the-thesis-layout/ 

# Attachments
## Model
```{r model code attachment, eval=FALSE}
# Rick Venema
# 368044
# k.f.venema@st.hanze.nl

########
# Libs #
########
library(deSolve)

###############
## functions ##
###############xx

# Define the parameters
parameters <- c(kd_Rm = 0.612, ks_Rm = 2.90, ks_r = 3.22,
                kd_R = 0.0572, D=53.409, k_on= 0.00329, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57, Rf = 0.49)


# Define the model function
volume <- function(t, y, parms){
  with(as.list(c(y, parms)), {
    dmRNA.R_dt <- ks_Rm * (1- (DR_N/ (IC50_Rm + DR_N)))- kd_Rm * mRNA.R
    dR_dt <- ks_r *  mRNA.R + Rf * k_re * DR_N - k_on * D * R - kd_R * R
    dDR_dt <- k_on * D * R -k_t * DR
    dDR_N_dt <- k_t * DR - k_re* DR_N
    return(list(c(dmRNA.R_dt, dR_dt, dDR_N_dt, dDR_dt)))
  }
  )
}

# Define the state
state <- c(mRNA.R = 4.74, R = 267, DR_N = 0, DR = 0)

# Define time sequence you want to run the model
times <- seq(0, 48,  by = 1)

# Run simulation using continuous approach
out  <- ode(times = times, y = state,   parms = parameters, func = volume, 
            method = "euler")
```



## Assignment 2

```{r assignment2}
# Bas Kasemir
# 367248
# b.h.n.kasemir@st.hanze.nl




# Define the new parameters
parameters.mRNA <- c(kd_Rm = 0.612, ks_Rm = 2.90, ks_r = 3.22,
                kd_R = 0.0572, D=53.409, k_on= 0.00329, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57, Rf = 0.49)


# Define the model function
volume.mRNA <- function(t, y, parms){
  with(as.list(c(y, parms)), {
    dmRNA.R_dt <- ks_Rm * (1- (DR_N/ (IC50_Rm + DR_N)))- kd_Rm *mRNA.R
    dR_dt <- ks_r *  mRNA.R + Rf * k_re * DR_N - k_on * R - kd_R * R
    dDR_dt <- k_on * R -k_t * DR
    dDR_N_dt <- k_t * DR - k_re* DR_N
    return(list(c(dmRNA.R_dt, dR_dt, dDR_N_dt, dDR_dt)))
  }
  )
}

# Define the state
state <- c(mRNA.R = 4.74, R = 267, DR_N = 0, DR = 0)

# Define time sequence you want to run the model
times <- seq(0, 48,  by = 1)

# Run simulation using continuous approach
out.mRNA  <- ode(times = times, y = state,   parms = parameters.mRNA, func = volume.mRNA, method = "euler")
out.mRNA <- as.data.frame(out.mRNA)
par(mfrow = c(2,2))
plot(out.mRNA$time, out.mRNA$mRNA.R, type="l", xlab="Time", ylab="receptor mRNA", sub="(a)", main = "Concentration of the receptor\nmRNA in the cell")
plot(out.mRNA$time, out.mRNA$R, type="l", xlab="Time", ylab="free receptor density", sub="(b)", main = "Concentration of free receptors\nin the cell")
plot(out.mRNA$time, out.mRNA$DR, type="l", xlab="Time", ylab="drug-receptor complex", sub="(c)", main="Concentration of MPL-receptor\ncomplex in the cell")
plot(out.mRNA$time, out.mRNA$DR_N, type="l", xlab="Time", ylab="activated receptor complex", sub="(d)", main = "Concentration of activated\nMPL-receptor complex \n in the nucleus")



#######################
# 3
#######################

parameters.k_on1 <- c(kd_Rm = 0.612, ks_Rm = 2.90, ks_r = 3.22,
                kd_R = 0.0572, D=53.409, k_on= 0.00329/5, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57, Rf = 0.49)

# Run simulation using continuous approach
out.k_on1  <- ode(times = times, y = state,   parms = parameters.k_on1, func = volume, method = "euler")

out.k_on1 <- as.data.frame(out.k_on1)
par(mfrow = c(2,2))
plot(out.k_on1$time, out.k_on1$mRNA.R, type="l", xlab="Time", ylab="receptor mRNA", sub="(a)", main = "Concentration of the receptor\nmRNA in the cell")
plot(out.k_on1$time, out.k_on1$R, type="l", xlab="Time", ylab="free receptor density", sub="(b)", main = "Concentration of free receptors\nin the cell")
plot(out.k_on1$time, out.k_on1$DR, type="l", xlab="Time", ylab="drug-receptor complex", sub="(c)", main="Concentration of MPL-receptor\ncomplex in the cell")
plot(out.k_on1$time, out.k_on1$DR_N, type="l", xlab="Time", ylab="activated receptor complex", sub="(d)", main = "Concentration of activated\nMPL-receptor complex \n in the nucleus")


parameters.k_on2 <- c(kd_Rm = 0.612, ks_Rm = 2.90, ks_r = 3.22,
                kd_R = 0.0572, D=53.409, k_on= 0.00329/2, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57, Rf = 0.49)

# Run simulation using continuous approach
out.k_on2  <- ode(times = times, y = state,   parms = parameters.k_on2, func = volume, method = "euler")

out.k_on2 <- as.data.frame(out.k_on2)
par(mfrow = c(2,2))
plot(out.k_on2$time, out.k_on2$mRNA.R, type="l", xlab="Time", ylab="receptor mRNA", sub="(a)", main = "Concentration of the receptor\nmRNA in the cell")
plot(out.k_on2$time, out.k_on2$R, type="l", xlab="Time", ylab="free receptor density", sub="(b)", main = "Concentration of free receptors\nin the cell")
plot(out.k_on2$time, out.k_on2$DR, type="l", xlab="Time", ylab="drug-receptor complex", sub="(c)", main="Concentration of MPL-receptor\ncomplex in the cell")
plot(out.k_on2$time, out.k_on2$DR_N, type="l", xlab="Time", ylab="activated receptor complex", sub="(d)", main = "Concentration of activated\nMPL-receptor complex \n in the nucleus")


parameters.k_on3 <- c(kd_Rm = 0.612, ks_Rm = 2.90, ks_r = 3.22,
                kd_R = 0.0572, D=53.409, k_on= 0.00329*2, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57, Rf = 0.49)

# Run simulation using continuous approach
out.k_on3  <- ode(times = times, y = state,   parms = parameters.k_on3, func = volume, method = "euler")

out.k_on3 <- as.data.frame(out.k_on3)
par(mfrow = c(2,2))
plot(out.k_on3$time, out.k_on3$mRNA.R, type="l", xlab="Time", ylab="receptor mRNA", sub="(a)", main = "Concentration of the receptor\nmRNA in the cell")
plot(out.k_on3$time, out.k_on3$R, type="l", xlab="Time", ylab="free receptor density", sub="(b)", main = "Concentration of free receptors\nin the cell")
plot(out.k_on3$time, out.k_on3$DR, type="l", xlab="Time", ylab="drug-receptor complex", sub="(c)", main="Concentration of MPL-receptor\ncomplex in the cell")
plot(out.k_on3$time, out.k_on3$DR_N, type="l", xlab="Time", ylab="activated receptor complex", sub="(d)", main = "Concentration of activated\nMPL-receptor complex \n in the nucleus")


parameters.k_on4 <- c(kd_Rm = 0.612, ks_Rm = 2.90, ks_r = 3.22,
                kd_R = 0.0572, D=53.409, k_on= 0.00329*5, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57, Rf = 0.49)

# Run simulation using continuous approach
out.k_on4  <- ode(times = times, y = state,   parms = parameters.k_on4, func = volume, method = "euler")

out.k_on4 <- as.data.frame(out.k_on4)
par(mfrow = c(2,2))
plot(out.k_on4$time, out.k_on4$mRNA.R, type="l", xlab="Time", ylab="receptor mRNA", sub="(a)", main = "Concentration of the receptor\nmRNA in the cell")
plot(out.k_on4$time, out.k_on4$R, type="l", xlab="Time", ylab="free receptor density", sub="(b)", main = "Concentration of free receptors\nin the cell")
plot(out.k_on4$time, out.k_on4$DR, type="l", xlab="Time", ylab="drug-receptor complex", sub="(c)", main="Concentration of MPL-receptor\ncomplex in the cell")
plot(out.k_on4$time, out.k_on4$DR_N, type="l", xlab="Time", ylab="activated receptor complex", sub="(d)", main = "Concentration of activated\nMPL-receptor complex \n in the nucleus")






parameters.k_re1 <- c(kd_Rm = 0.612, ks_Rm = 2.90, ks_r = 3.22,
                kd_R = 0.0572, D=53.409, k_on= 0.00329, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57/5, Rf = 0.49)

# Run simulation using continuous approach
out.k_re1  <- ode(times = times, y = state,   parms = parameters.k_re1, func = volume, method = "euler")

out.k_re1 <- as.data.frame(out.k_re1)
par(mfrow = c(2,2))
plot(out.k_re1$time, out.k_re1$mRNA.R, type="l", xlab="Time", ylab="receptor mRNA", sub="(a)", main = "Concentration of the receptor\nmRNA in the cell")
plot(out.k_re1$time, out.k_re1$R, type="l", xlab="Time", ylab="free receptor density", sub="(b)", main = "Concentration of free receptors\nin the cell")
plot(out.k_re1$time, out.k_re1$DR, type="l", xlab="Time", ylab="drug-receptor complex", sub="(c)", main="Concentration of MPL-receptor\ncomplex in the cell")
plot(out.k_re1$time, out.k_re1$DR_N, type="l", xlab="Time", ylab="activated receptor complex", sub="(d)", main = "Concentration of activated\nMPL-receptor complex \n in the nucleus")


parameters.k_re2 <- c(kd_Rm = 0.612, ks_Rm = 2.90, ks_r = 3.22,
                kd_R = 0.0572, D=53.409, k_on= 0.00329, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57/2, Rf = 0.49)

# Run simulation using continuous approach
out.k_re2  <- ode(times = times, y = state,   parms = parameters.k_re2, func = volume, method = "euler")

out.k_re2 <- as.data.frame(out.k_re2)
par(mfrow = c(2,2))
plot(out.k_re2$time, out.k_re2$mRNA.R, type="l", xlab="Time", ylab="receptor mRNA", sub="(a)", main = "Concentration of the receptor\nmRNA in the cell")
plot(out.k_re2$time, out.k_re2$R, type="l", xlab="Time", ylab="free receptor density", sub="(b)", main = "Concentration of free receptors\nin the cell")
plot(out.k_re2$time, out.k_re2$DR, type="l", xlab="Time", ylab="drug-receptor complex", sub="(c)", main="Concentration of MPL-receptor\ncomplex in the cell")
plot(out.k_re2$time, out.k_re2$DR_N, type="l", xlab="Time", ylab="activated receptor complex", sub="(d)", main = "Concentration of activated\nMPL-receptor complex \n in the nucleus")


parameters.k_re3 <- c(kd_Rm = 0.612, ks_Rm = 2.90, ks_r = 3.22,
                kd_R = 0.0572, D=53.409, k_on= 0.00329, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57*5, Rf = 0.49)

# Run simulation using continuous approach
out.k_re3  <- ode(times = times, y = state,   parms = parameters.k_re3, func = volume, method = "euler")

out.k_re3 <- as.data.frame(out.k_re3)
par(mfrow = c(2,2))
plot(out.k_re3$time, out.k_re3$mRNA.R, type="l", xlab="Time", ylab="receptor mRNA", sub="(a)", main = "Concentration of the receptor\nmRNA in the cell")
plot(out.k_re3$time, out.k_re3$R, type="l", xlab="Time", ylab="free receptor density", sub="(b)", main = "Concentration of free receptors\nin the cell")
plot(out.k_re3$time, out.k_re3$DR, type="l", xlab="Time", ylab="drug-receptor complex", sub="(c)", main="Concentration of MPL-receptor\ncomplex in the cell")
plot(out.k_re3$time, out.k_re3$DR_N, type="l", xlab="Time", ylab="activated receptor complex", sub="(d)", main = "Concentration of activated\nMPL-receptor complex \n in the nucleus")


parameters.k_re4 <- c(kd_Rm = 0.612, ks_Rm = 2.90, ks_r = 3.22,
                kd_R = 0.0572, D=53.409, k_on= 0.00329, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57*2, Rf = 0.49)

# Run simulation using continuous approach
out.k_re4  <- ode(times = times, y = state,   parms = parameters.k_re4, func = volume, method = "euler")

out.k_re4 <- as.data.frame(out.k_re4)
par(mfrow = c(2,2))
plot(out.k_re4$time, out.k_re4$mRNA.R, type="l", xlab="Time", ylab="receptor mRNA", sub="(a)", main = "Concentration of the receptor\nmRNA in the cell")
plot(out.k_re4$time, out.k_re4$R, type="l", xlab="Time", ylab="free receptor density", sub="(b)", main = "Concentration of free receptors\nin the cell")
plot(out.k_re4$time, out.k_re4$DR, type="l", xlab="Time", ylab="drug-receptor complex", sub="(c)", main="Concentration of MPL-receptor\ncomplex in the cell")
plot(out.k_re4$time, out.k_re4$DR_N, type="l", xlab="Time", ylab="activated receptor complex", sub="(d)", main = "Concentration of activated\nMPL-receptor complex \n in the nucleus")


##################
# 4
##################

parameters.blocked <- c(kd_Rm = 0.612, ks_Rm = 2.90, ks_r = 3.22,
                kd_R = 0.0572, D=53.409, k_on= 0, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57, Rf = 0.49)

# Run simulation using continuous approach
out.blocked  <- ode(times = times, y = state,   parms = parameters.blocked, func = volume, method = "euler")

out.blocked <- as.data.frame(out.blocked)
par(mfrow = c(2,2))
plot(out.blocked$time, out.blocked$mRNA.R, type="l", xlab="Time", ylab="receptor mRNA", sub="(a)", main = "Concentration of the receptor\nmRNA in the cell")
plot(out.blocked$time, out.blocked$R, type="l", xlab="Time", ylab="free receptor density", sub="(b)", main = "Concentration of free receptors\nin the cell")
plot(out.blocked$time, out.blocked$DR, type="l", xlab="Time", ylab="drug-receptor complex", sub="(c)", main="Concentration of MPL-receptor\ncomplex in the cell")
plot(out.blocked$time, out.blocked$DR_N, type="l", xlab="Time", ylab="activated receptor complex", sub="(d)", main = "Concentration of activated\nMPL-receptor complex \n in the nucleus")




##################
# 5
##################

para.5.1 <- c(kd_Rm = 2.9/5/4.74, ks_Rm = 2.9/5, ks_r = 3.22,
                kd_R = 0.0572, D=53.409, k_on= 0.00329, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57, Rf = 0.49)

# Run simulation using continuous approach
out.5.1  <- ode(times = times, y = state,   parms = para.5.1, func = volume, method = "euler")

out.5.1 <- as.data.frame(out.5.1)
par(mfrow = c(2,2))
plot(out.5.1$time, out.5.1$mRNA.R, type="l", xlab="Time", ylab="receptor mRNA", sub="(a)", main = "Concentration of the receptor\nmRNA in the cell")
plot(out.5.1$time, out.5.1$R, type="l", xlab="Time", ylab="free receptor density", sub="(b)", main = "Concentration of free receptors\nin the cell")
plot(out.5.1$time, out.5.1$DR, type="l", xlab="Time", ylab="drug-receptor complex", sub="(c)", main="Concentration of MPL-receptor\ncomplex in the cell")
plot(out.5.1$time, out.5.1$DR_N, type="l", xlab="Time", ylab="activated receptor complex", sub="(d)", main = "Concentration of activated\nMPL-receptor complex \n in the nucleus")

para.5.2 <- c(kd_Rm = 2.9/2/4.74, ks_Rm = 2.9/2, ks_r = 3.22,
                kd_R = 0.0572, D=53.409, k_on= 0.00329, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57, Rf = 0.49)

# Run simulation using continuous approach
out.5.2  <- ode(times = times, y = state,   parms = para.5.2, func = volume, method = "euler")

out.5.2 <- as.data.frame(out.5.2)
par(mfrow = c(2,2))
plot(out.5.2$time, out.5.2$mRNA.R, type="l", xlab="Time", ylab="receptor mRNA", sub="(a)", main = "Concentration of the receptor\nmRNA in the cell")
plot(out.5.2$time, out.5.2$R, type="l", xlab="Time", ylab="free receptor density", sub="(b)", main = "Concentration of free receptors\nin the cell")
plot(out.5.2$time, out.5.2$DR, type="l", xlab="Time", ylab="drug-receptor complex", sub="(c)", main="Concentration of MPL-receptor\ncomplex in the cell")
plot(out.5.2$time, out.5.2$DR_N, type="l", xlab="Time", ylab="activated receptor complex", sub="(d)", main = "Concentration of activated\nMPL-receptor complex \n in the nucleus")

para.5.3 <- c(kd_Rm = 2.9*2/4.74, ks_Rm = 2.9*2, ks_r = 3.22,
                kd_R = 0.0572, D=53.409, k_on= 0.00329, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57, Rf = 0.49)

# Run simulation using continuous approach
out.5.3  <- ode(times = times, y = state,   parms = para.5.3, func = volume, method = "euler")

out.5.3 <- as.data.frame(out.5.3)
par(mfrow = c(2,2))
plot(out.5.3$time, out.5.3$mRNA.R, type="l", xlab="Time", ylab="receptor mRNA", sub="(a)", main = "Concentration of the receptor\nmRNA in the cell")
plot(out.5.3$time, out.5.3$R, type="l", xlab="Time", ylab="free receptor density", sub="(b)", main = "Concentration of free receptors\nin the cell")
plot(out.5.3$time, out.5.3$DR, type="l", xlab="Time", ylab="drug-receptor complex", sub="(c)", main="Concentration of MPL-receptor\ncomplex in the cell")
plot(out.5.3$time, out.5.3$DR_N, type="l", xlab="Time", ylab="activated receptor complex", sub="(d)", main = "Concentration of activated\nMPL-receptor complex \n in the nucleus")

para.5.4 <- c(kd_Rm = 2.9*5/4.74, ks_Rm = 2.9*5, ks_r = 3.22,
                kd_R = 0.0572, D=53.409, k_on= 0.00329, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57, Rf = 0.49)

# Run simulation using continuous approach
out.5.4  <- ode(times = times, y = state,   parms = para.5.4, func = volume, method = "euler")

out.5.4 <- as.data.frame(out.5.4)
par(mfrow = c(2,2))
plot(out.5.4$time, out.5.4$mRNA.R, type="l", xlab="Time", ylab="receptor mRNA", sub="(a)", main = "Concentration of the receptor\nmRNA in the cell")
plot(out.5.4$time, out.5.4$R, type="l", xlab="Time", ylab="free receptor density", sub="(b)", main = "Concentration of free receptors\nin the cell")
plot(out.5.4$time, out.5.4$DR, type="l", xlab="Time", ylab="drug-receptor complex", sub="(c)", main="Concentration of MPL-receptor\ncomplex in the cell")
plot(out.5.4$time, out.5.4$DR_N, type="l", xlab="Time", ylab="activated receptor complex", sub="(d)", main = "Concentration of activated\nMPL-receptor complex \n in the nucleus")

```

[4] k.on moet op 0 gezet worden. Dit is de snelheid waarmee het complex gesynthetiseerd worden.
=======

## Model validation
```{r model validation attachement, echo = T, eval=FALSE }
# Rick Venema
# 368044
# k.f.venema@st.hanze.nl

############
# The Data #
############
# Read data from CSV file
data <- read.csv("MPL.csv", na.strings = "NA")

# Store trimmed data for dose 0.1 and dose 0.3
data_0.1 <- data[data$dose == 0.1,]
data_0.3 <- data[data$dose == 0.3,]

# Calculate the median of the cocentration MPL for dose 0.1 and dose 0.3
median_MPL_0.3 <- median(data$MPL_conc[data$dose==0.3], na.rm = T)
median_MPL_0.1 <- median(data$MPL_conc[data$dose==0.1], na.rm = T)

# Store trimmed data for dose 0.1 and dose 0.3
D_0.3 <- median_MPL_0.3*1000/374.471
D_0.1 <- median_MPL_0.1*1000/374.471

####
# Model with parameters responding with experiment
#
parameters0.3 <- c(kd_Rm = 0.612, ks_Rm = 2.90, ks_r = 3.22,
                kd_R = 0.0572, D= D_0.3, k_on= 0.00329, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57, Rf = 0.49)

parameters0.1 <- c(kd_Rm = 0.612, ks_Rm = 2.90, ks_r = 3.22,
                kd_R = 0.0572, D= D_0.1, k_on= 0.00329, IC50_Rm = 26.2,
                k_t = 0.63, k_re = 0.57, Rf = 0.49)

state0.3 <- c(mRNA.R = 4.74, R = 267, DR_N = 0, DR = 0)
state0.1 <- c(mRNA.R = 4.74, R = 267, DR_N = 0, DR = 0)

times <- seq(0, 175,  by = 1)


# Run simulation using continuous approach
out0.3  <- ode(times = times, y = state0.3,   parms = parameters0.3, 
               func = volume, method = "euler")
out0.3 <- as.data.frame(out0.3)

out0.1  <- ode(times = times, y = state0.1,   parms = parameters0.1, 
               func = volume, method = "euler")
out0.1 <- as.data.frame(out0.1)

medians <- aggregate(data[,c("MPL_conc","mRNA","Free_receptor")],
                     list(data$dose,data$time), median, na.rm=T)
names(medians)[1:2] <- c("dose","time")

dose_0.3 <- medians[medians$dose==0.3,]
dose_0.1 <- medians[medians$dose==0.1,]
```

