---
title: High organic inputs explain shallow and deep SOC storage in a long-term agroforestry
  system - combining experimental and modeling approaches 
author: "Rick Venema & Bas Kasemir"
date: "`r Sys.Date()`"

output: 
  pdf_document:
    toc: False
    number_sections: True
  includes:
    in_header: latex/header.tex
    before_body: latex/before_body.tex
    after_body: latex/after_body.tex

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


\newpage
\tableofcontents
\newpage


# Introduction BAS
This paper is about SOC (soil organic carbon) storage and the improvement of existing models. The model that is created in the original paper is describing the flow of carbon in the soil and trees next to the measured points. This original model contains different models from several other papers. The code used in this model is not written very efficiently. It takes too much time to run the model and all the data is hardcoded and thereby not easy adjustable, which is nescesary for a good model to use for simulation of changes of certain values.
We have requested the code for the model from Remi Ceardinal (author of the paper $papername). We have build the code and tested it on several computers. The first thing we noticed was a very long runningtime (the model contained many if statements and for loops in for loops). Next to that, all the data is entered hardcoded and so it was not suitable for adjusting and extending on the model.
We decided to rewrite the whole model achieving a much shorter running time and possibilty to use ajustable parameters.
  


---------eerst het onderwerp / probleem (niet vermelden dat we opnieuw doen) verleiden met eerste zin om het te lezen. 2e zin geeft context, probleem. (het versimpelen van bestaand model) doel

Achtergrond 
waar zijn we mee bezig/wat is gedaan (context)

problemen (voorbereidend op wat je zelf gaat doen)
-> studie (dit gaan we doen)

indeling verslag (wat de lezer tegen kan komen)

\newpage
# Materials and methods
To create a valid model, the model must need to account the depth, distance from the tree and the time in years. This can be done with partial differential equations. The model is based on several other models that are borrowed   **WE GEBRUIKEN GEEN LENEN HIER** from other researches.
First the received code is printed out and piece by piece stripped down to understand what was going on. After this the code had been split up in parts and these have been rewritten


/////INSERT IMAGE//////

welke methode gebruik ik wat 


waar komt data/model vandaan model = visueel = formules

Aanpak / variatie 

Analyse 
wel in verhaaltje vertellen.

## The Model
The model is defined in the paper by Cardinael et al. (2018), this model follows a three pool model. 

The fresh organic compound (FOC) difference can be found in formula \ref{eq:deltafoc}.
\begin{equation} \label{eq:deltafoc}
\frac{\delta FOC_{t,z,d}}{\delta t} = I_{t,z,d} + \frac{\delta F_{AD}}{\delta z} + h * f_{2}* dec\_HSOC_{t,z,d} + h *dec\_HSOC2_{tzd} - dec\_FOC_{t,z,d} 
\end{equation}


\begin{equation} \label{eq:deltahsoc1}
 \frac{\delta HSOC1}{\delta t} = \frac{\delta F_{AD}}{\delta z} + h * f_{1} * dec\_FOC_{t,z,d} - dec\_HSOC1_{t,z,d}
\end{equation}

\begin{equation} \label{eq:deltahsoc2}
  \frac{\delta HSOC2}{\delta t} = \frac{\delta F_{AD}}{\delta z} + h * (1-f_{1}) * dec\_FOC_{t,z,d} + h *(1-f_{2})*dec\_HSOC1_{t,z,d} - dec\_HSOC2_{t,z,d}
\end{equation}




# Results
```{r test of import, message=F, echo=F, warning=F}
source(file="three-pool-model.R")
``` 


grafieken met onderschrift en uitleg over wat er te zien is

# Discussion
conclusie van het verhaal, hoe was het goed uit te voeren?, waarom niet helemaal belicht, verschil.

# Conclusion

# References
1. Cardinael, R., Guenet, B., Chevallier, T., Dupraz, C., Cozzi, T., and Chenu, C.: High organic imputs explain shallow and deep SOC storage in a long-term agroforestry system - combining experimental and modeling approaches, Biogeosciences, 15, 297-317, https://di.org/10.5194/bg-15-297-2018, 2018.
2. Soetaert, K., Petzoldt, T., and Woodrow Setzer, R.: Solving differential equations in R: package deSolve, J. Stat. Softw., 33, 1-25, 2010.
