---
title: High organic inputs explain shallow and deep SOC storage in a long-term agroforestry
  system - combining experimental and modeling approaches 
author: "Rick Venema & Bas Kasemir"
date: "`r Sys.Date()`"

output: 
  pdf_document:
    toc: False
    number_sections: True
  includes:
    in_header: latex/header.tex
    before_body: latex/before_body.tex
    after_body: latex/after_body.tex

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


\newpage
\tableofcontents
\newpage


# Introduction
This paper is based around the reproduction of the paper by Cardinal et al. (2018). This paper is about SOC (soil organic carbon) storage. This is the amount of carbon in the soil. The model that is created in that paper contains different models describing the flow of carbon in the soil and trees next to it. 


waar zijn we mee bezig, uitbreiden, opnieuw doen

# Materials and methods
To create a valid model, the model must need to account the depth, distance from the tree and the time in years. This can be done with partial differential equations.

welke methode gebruik ik wat 

## The Model
The model is defined in the paper by Cardinal et al. (2018), this model follows a three pool model. 

The fresh organic compound (FOC) difference can be found in formula \ref{eq:deltafoc}.
\begin{equation} \label{eq:deltafoc}
\frac{\delta FOC_{t,z,d}}{\delta t} = I_{t,z,d} + \frac{\delta F_{AD}}{\delta z} + h * f_{2}* dec\_HSOC_{t,z,d} + h *dec\_HSOC2_{tzd} - dec\_FOC_{t,z,d} 
\end{equation}


\begin{equation} \label{eq:deltahsoc1}
 \frac{\delta HSOC1}{\delta t} = \frac{\delta F_{AD}}{\delta z} + h * f_{1} * dec\_FOC_{t,z,d} - dec\_HSOC1_{t,z,d}
\end{equation}

\begin{equation} \label{eq:deltahsoc2}
  \frac{\delta HSOC2}{\delta t} = \frac{\delta F_{AD}}{\delta z} + h * (1-f_{1}) * dec\_FOC_{t,z,d} + h *(1-f_{2})*dec\_HSOC1_{t,z,d} - dec\_HSOC2_{t,z,d}
\end{equation}




## The Parameters and Starting Values
\begin {table}[!h]
\caption{Table showing the parameters used} \label{tab:parameters}
\begin{center} 
    \begin{tabular}{ l | l }
    \hline 
    \multicolumn{2}{c}{\textbf{\textsl{Parameters}}} \\ [0.5ex]
    \hline
    \emph{Parameter} & \emph{value} \\ \hline
    $I_{t,z,d}$ & 0.69 \\ \hline
    Tuesday & 9C   \\ \hline
    Wednesday & 10C \\ 
    \hline
    \end{tabular}
\end{center}
\end{table}


# Results
```{r test of import, message=F, echo=F, warning=F}
source(file="three-pool-model.R")
``` 

# Discussion
conclusie van het verhaal, hoe was het goed uit te voeren?, waarom niet helemaal belicht, verschil.

# Conclusion

# References
1. Cardinael, R., Guenet, B., Chevallier, T., Dupraz, C., Cozzi, T., and Chenu, C.: High organic imputs explain shallow and deep SOC storage in a long-term agroforestry system - combining experimental and modeling approaches, Biogeosciences, 15, 297-317, https://di.org/10.5194/bg-15-297-2018, 2018.
2. Soetaert, K., Petzoldt, T., and Woodrow Setzer, R.: Solving differential equations in R: package deSolve, J. Stat. Softw., 33, 1-25, 2010.
