---
title: "Rewrite Log Rick"
author: "Rick Venema"
date: "`r Sys.Date()`"
output:
  pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction
The model we have recieved from Remi Cardinael from Cardinael et al 2018 was based around the SOC stocks in an Agroforestry plot containing walnut trees and durum wheat. 

## References
1. Cardinael, R., Guenet, B., Chevallier, T., Dupraz, C., Cozzi, T., and Chenu, C.: High organic imputs explain shallow and deep SOC storage in a long-term agroforestry system - combining experimental and modeling approaches, Biogeosciences, 15, 297-317, https://di.org/10.5194/bg-15-297-2018, 2018.

# 7-6-2018
This was the first day we started rewriting the code given by Cardinael. This code was around 948 lines long. 
The model was a hard coded model of the reality of that specific tree. We decided that we wanted to rewrite the model. 
This was because of the first intention to add the nitrogen cycle to the model was not easy because of the bad coding we recieved. So in order to add the Nitrogen model, the model needs to be rewritten so it can be used to generate a model based on parameters instead of fixed data.
```{r 7-6-18a, eval=F}
modelp3difft <- function(t, initial_state, parms){
  with (as.list(parms),{
          A <- initial_state[1:dim(z)[1]]
          S <- initial_state[(dim(z)[1]+1):((2*dim(z)[1]))]
          P <- initial_state[((2*dim(z)[1])+1):((3*dim(z)[1]))]  
          
          #Fluxes in z direction
          FluxA <- Dt * (c(0,A))/dz -D * diff(c(0,A,0)) / dz - c(0,Dmix) * diff(c(0,A,0)) / dz 
          FluxS <- Dt * (c(0,S))/dz -D_slow*diff(c(0,S,0)) / dz - c(0,Dmix) * diff(c(0,S,0)) / dz
          FluxP <- Dt * (c(0,P))/dz -D_slow*diff(c(0,P,0)) / dz - c(0,Dmix) * diff(c(0,P,0)) / dz
          FluxA[1]=0.
          FluxS[1]=0.
          FluxP[1]=0.
          
          #Reaction       
          Import<-import_tree_be*mr_tree + import_grass_be*mr_grass + import_crop_be*mr_crop
          dA=-diff(FluxA) + (e*ks*S*frac_SA + e*kp*P - kf* A* clay_func)* mf* tf  + Import
          dS=-diff(FluxS) + (frac_AS*kf*e*A*clay_func - ks*S)* mf* tf
          dP=-diff(FluxP) + ((1-frac_SA)*e*ks*S + (1-frac_AS)*kf*e*A*clay_func - kp*P)* mf* tf
          
          return(list(c(dA=dA,dS=dS,dP=dP)))
        })
}
```
Above, the model is given. This is the model what generates the output.
  
In the original code `PARAM=read.table('run_options_p0_3pools.def', header=FALSE)` can be found. This file contains only numbers and thus can be added to the model as a vector to adjust parameter even more. The PARAM part can also be ommited to give the parameters their respective values directly instead of being loaded from a file and then passed as a dataframe. The original code called the PARAM variable by `parameter = PARAM[i,1]/10000. `. This is unreadable for himself when he tries to debug this code. It is easier to give the parameters directly with their correct values. An example follows below:

```{r 7-6-18b, eval=F}
### Code with PARAM as hard coded vector
PARAM <-  c(0.01, 0.83, 5.24, 21.60, 0.34, 0.99, 0.94)
Dt=PARAM[4]/10000.
D_slow = PARAM[3]/10000.

### Code with values directly added to variable
Dt = 21.60/10000.
D_slow = 5.24/10000.
```






